\section{Introduction}
\label{sec:introduction}
	This report present the opposition for the Master's Thesis 
	\textit{Model Predicitive Control of a Tricopter} by Karl-Johan Barsk, written
	during the spring semester of 2012 at Linköping University.

\subsection{Thesis Outline}
	The thesis presents the identification and control of a tricopter UAV.
	Three different models are proposed, identified and evaluated in the 
	thesis, and used for state estimation and MPC control. 
	
	Two variants of MPC are evaluated: explicit MPC and Fast Gradient MPC.
	Each of the variants are tested on a microcontroller using code generated
	from \textsc{Matlab}.
	
	The proposed MPC controllers focus on stabilizing the angular rates of
	the tricopter, following the reference of a pilot.

\subsection{General Comments}
	The thesis covers an interesting subject in a very demanding type of 
	application - not least because of the computational limitations of the system.
	The report is very well structured, and the workflow is easily followed 
	through the report.

	The citation style used in the thesis - text without brackets - sometime makes
	it quite difficult to know when a citation is referenced, and sometimes even
	makes for very strange sentences\footnote{Example from p. 21: ``\textit{... and then inverting Gustafsson ...''}}.

	In some later parts of the report, the text is somewhat too implementation-specific,
	explicitly defining the \textsc{Matlab} commands that were used. 
	While detail is not nescessarily wrong, it receives too much focus, 
	especially in the \textit{Controller}-chapter.

	The report is well supported by good figures and relevant choices of
	plots.
